Correlation Clustering with Dynamic Super-Nodes (DySNCC)

### 2014-10-23 paper/egpaper_for_review.tex
update scatterplot

\input{tables/anytime/knott-3d-450.tex}
\begin{figure*}
\input{scatterplots/knott-3d-450.tex}
\end{figure*}

>>>>

\input{tables/anytime/knott-3d-450.tex}
\begin{figure}
\input{scatterplots/knott-3d-450.tex}
\caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
A more aggressive one would lead to much faster runtime with only a bit worse values.
DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
}
\end{figure}

### 2014-10-23 paper/scatterplots/knott-3d-450.tex
update scatterplot

  \begin{axis}[

@@

  %  xmax = 400,
  %  ymax = 1000,

@@

    width = 0.95\textwidth, 
    height= 0.95\textwidth, 

@@

  \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{ogm-ICM};   
  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath knott-3d-450.data}; 

@@

  \addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{ogm-LF-1};   
  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-B};   
  \addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-B-CGC};   
  \addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-CGC};   
  \addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 

@@

  \addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-MC};   
  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 

@@

  \addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-B};   
  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-B-CGC};   
  \addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-CGC};   
  \addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-CGC-CGC};   
  \addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-MC};   
  \addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-MC-CGC};   
  \addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath knott-3d-450.data}; 

@@

  \addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCR-CCFDB};   
  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCR-CCFDB-OWC};   
  \addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCI-CCFDB-CCIFD};   
  \addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath knott-3d-450.data}; 

@@

  \addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath knott-3d-450.data}; 

@@

  \end{axis} 

>>>>

  \begin{loglogaxis}[

@@

@@

    width = 0.95\columnwidth, 
    height= 0.95\columnwidth, 

@@

 % \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_HC, y=Vogm_HC]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{HC};   
  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_HC_CGC, y=Vogm_HC_CGC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{HC-CGC};   
  %\addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{ogm-ICM};   
  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath knott-3d-450.data}; 

@@

  %\addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{ogm-LF-1};   
  %\addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-HC-B};   
  %\addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-HC-B-CGC};   
  %\addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-HC-CGC};   
  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 

@@

  %\addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-HC-MC};   
  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 

@@

  %\addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-WS-B};   
  %\addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-WS-B-CGC};   
  %\addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-WS-CGC};   
  %\addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-WS-CGC-CGC};   
  %\addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-WS-MC};   
  %\addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{DYNCC-WS-MC-CGC};   
  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath knott-3d-450.data}; 

@@

  %\addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{MCR-CCFDB};   
  %\addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{MCR-CCFDB-OWC};   
  %\addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath knott-3d-450.data}; 
  %\addlegendentry{MCI-CCFDB-CCIFD};   
  \addplot[only marks, mark=square*,orange!50, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath knott-3d-450.data}; 

@@

  \addplot[only marks, mark=square*,cyan, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath knott-3d-450.data}; 

@@

  \end{loglogaxis} 
